Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation

### 2023-05-15 index.qmd
add example page

The intention was, according to the publishers, to draw attention **to people who were at the height of their activities**, even if they were younger in influential or otherwise noted positions in different areas.

@@

@@

## Vem är Vem? Example

>>>>

The intention was, according to the publishers, to draw attention **to people who were at the height of their activities**, even if they were younger, in influential or otherwise noted positions in different areas.

@@

## Vem är Vem? Example page

![](assets/vem_page.png){fig-align="center" width=100%}

@@

## Vem är Vem? Example biography
